(Placeholder) Automatic selection of kinase expression constructs

### 2016-01-27 manuscript/ms.tex
Added Macrolab expression testing method

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

High-throughput cloning was performed using LIC (Ligation Independent Cloning). {\color{blue}[LRL: There wasn't any details on how the Macrolab performed the cloning in the p470 Kinase Expression Testing Report. But I read in their website that this is the method commonly used.]}
Single colonies of transformants were cultivated with 900 uL of MagicMedia into a gas permeable sealed 96-well block. 
The cultures were incubated at 37 C for 4 hours and then at 16 C for 40 hours while shacking. 
Next, cells were centrifuged and the pellets were frozen at -80 C overnight. 
Cells were lysed on a rotating platform at room temperature for an hour using 700 uL of Solulyse (Genlantis) supplemented with 400 mM NaCl, 20 mM imidazole and protease inhibitors. 
For protein purification, 500 uL of the soluble lysate was added to a 25 uL Ni-NTA resin in a 96-well filter plate. 
Nickel Buffer A (25 mM HEPES pH 7.5, 5\% glycerol, 400 mM NaCl, 20 mM imidazole, 1 mM BME) was added and the plate was mixed for 30 minutes at room temperature. 
The resin was washed with 2 mL of Nickel Buffer A. 
Target proteins were eluted by a 2 hour incubation at room temperature with 10 ug of TEV protease in 80 uL of Nickel Buffer A.
A subsequent wash with 40 uL of Nickel Buffer A was performed to release more target protein. 
Nickel Buffer B (25 mM HEPES pH 7.5, 5\% glycerol, 400 mM NaCl, 400 mM imidazole, 1 mM BME) was used to elute TEV resistant material remaining on the resin.
Untagged protein eluted with TEV protease was run on a LabChip GX II Microfluidic system to analyze the mayor protein species present. 
Samples of total cell lysate, soluble cell lysate and Nickel Buffer B elution were run on a SDS-PAGE for analysis. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
